---
title: 'Re: Bottle Machine'
output: html_document
params: 
  factory:
    value: Dublin
    choices:
      - Dublin
      - London 
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)

filename <- switch(params$factory,
  Dublin = "dublin.csv",
  London = "london.csv")
samples <- read_csv(here("data", filename))
sample_mean <- mean(samples$amount)
```

Does our bottle machine fill each bottle with 750 mL of beer (on average)?

## Data

I selected 50 bottles at random from the `r params$factory` factory, which contained the following amounts of beer (mL):

```{r echo = FALSE}
samples$amount
```

The mean amount is **`r sample_mean`**.

## Reasoning

The amounts of beer in our bottles should be normally distributed with a mean of 750 mL and a standard deviation of 3 mL. Let's use simulation to calculate the sample means of 1000 samples of size 50 generated from such a distribution.

```{r echo = FALSE}
bootstrap_means <- replicate(1000, mean(rnorm(50, mean = 750, sd = 3)))
delta <- abs(750 - sample_mean)
bootstrap_deltas <- abs(750 - bootstrap_means)
pvalue <- mean(bootstrap_deltas >= delta)
```

```{r echo = FALSE, fig.height = 2}
ggplot() +
  geom_histogram(aes(x = bootstrap_means), bins = 30) +
  geom_rect(aes(xmin = -Inf, xmax = 750 - delta, 
                ymin = -Inf, ymax = Inf), 
            fill = "#4197D9", alpha = 0.2) +
  geom_rect(aes(xmin = 750 + delta, xmax = Inf, 
                ymin = -Inf, ymax = Inf),
            fill = "#4197D9", alpha = 0.2) +
  geom_vline(aes(xintercept = sample_mean), 
             color = "#4197D9", size = 3)
```

I've plotted the distribution of the simulated means above. The blue line shows our observed sample mean. Notice that `r paste0(pvalue * 100, "%")` of the simulations produced a sample mean as extreme as ours (p-value = `r pvalue`). In other words, our observations `r ifelse(pvalue <= 0.05, "seem unlikely to have happened if the machine is functioning correctly", "are in accordance with our belief")`.

## Conclusion

We `r ifelse(pvalue <= 0.05, "", "do **not**")` have evidence that the bottle machine is malfunctioning.
